An Improved ANS Transaction Template

### 2018-01-26 paper.tex
done with the assay section

\subsection{Relevant Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{fig:assay_c1_nc} and \ref{fig:assay_c2_nc}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling.}\label{fig:assay_c1_nc}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling.}\label{fig:assay_c2_nc}
\end{figure}

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ as a function of the cascade level and the
  case considered.}
  \label{tab:cascade_theta}
\end{table}
As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
different level increase up to $0.54$ for the fifth stage on case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

\subsubsection{tails recycling}

\subsubsection{Case 1}
As shows on Figure \ref{ }, without tails recycling, the number of cascade level
required to enrich the uranium up to $90\%$ are respectively 5 for the
first case considered. Recycling the tails, allow to reduce the number of
enrichment levels required to enrich natural uranium up to a high enrich level
to 3.

This bump in enrichment can easily be explained, as the cascade does not have the
same number of stages, there is less stripping enrichment work, than enriching
work. That is to say that even work in an ideal case (where the stripping work of a
stage is the exact inverse of the enrich work), with an cascade with less
stripping stage than enriching stage will produce tail with a higher enrichment
than the feed of the previous level of

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Results and Analysis}

>>>>

\subsection{Explored Cases}
\subsubsection{Reference Case}
The reference case corresponds to the most ideal cascade design--utilizing all the 5060
centrifuges available within JCPOA to produce an enriched product at $>90\%$ of U-235,
stripping the tail product up to 0.28 $\%$ from a feed of natural uranium.
The design cascade in this case, includes 4 stripping stages, and 38 enriching
stages. The Feed/Product/Tail (F/P/T) assay are respectively
0.0071/0.903/0.0028.
%maybe include some cascade shape figures?

@@

\section{Results}
\subsection{Enrichment}
\subsubsection{Without tail recycling}
Despite the reconfiguration of each level occurring in the second case, the case
1 is way more effective to produce HEU than case 1.Indeed as observed on Figure
\ref{fig:assay_c1_nr} and \ref{fig:assay_c2_nr}, the first case is able to
produce an uranium product enrich at $98\%$ while the second case is only able
to reach an enrichment of $88.3\%$.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_nr}
\end{figure}
\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_no_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 without recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_nr}
\end{figure}

@@

\bottomrule
\end{tabular}
  \caption{Cascade effective $\theta$ by the level and the case.}
  \label{tab:cascade_theta}
\end{table}
As illustrated on Table \ref{tab:cascade_theta} the effective cut of the
different level increase up to $0.54$ for the fifth stage on case 2. The high
effective cut value increase the product production rate but decrease the
enrichment ratio.

\subsubsection{tails recycling}
When recycling the tails from the different cascade levels, both cases behave
the same way. As the tails have an higher enrichment than the product then are
blended to, recycling the tail has the effect to bump up the enrichment of the
product at each level (see Figure \ref{fig:assay_c1_r} and \ref{fig:assay_c2_r}).

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_1_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 1 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c1_r}
\end{figure}

Note that for the case 2, where the fourth stage could appear as useless only the
blending of its tail allows the product of the third one to pass the $90\%$ threshold.

\begin{figure}[ht] % replace 't' with 'b' to force it to be on the bottom
  \centering
  \includegraphics[width=0.5\textwidth]{assay_case_2_rec.png}
  \caption{Evolution of the different product assays at each cascade level for
  the case 2 with recycling. The blue line represents the $90\%$ enrichment
  threshold.}\label{fig:assay_c2_r}
\end{figure}

\subsection{HEU flow rate}
